---
title: "Code to generate the figures from Abbatecola et al.'s Face-Voice noise and attention article"
output:
    html_document:
    number_sections: true
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

# Figure 1

## 1B

```{r 1B, fig.width=6, fig.height=8}

require(lattice)
require(latticeExtra)

d <- read.csv("./data/exp_att/nonpar_scales.csv", 
              stringsAsFactors = TRUE)

complev <- strsplit(as.character(d$level), "_")
d$Comp <- factor(sapply(complev, "[", 1))
d$StimLev <- as.integer(sapply(complev, "[", 2))
d$subID <- factor(d$subID)
d$oscale <- d$scale + 1

dd <- subset(d, subID %in% c(6, 28, 34)) |> droplevels()

d$task <- factor(d$task, levels = c("fac", "voi", "sti"))
dd$task <-  factor(dd$task, levels = c("fac", "voi", "sti"))
levels(dd$task) <- levels(d$task) <- c("Face", "Voice", "Stimulus")
d$Comp <- factor(d$Comp, levels = c("fac", "voi"))
dd$Comp <- factor(dd$Comp, levels = c("fac", "voi"))
levels(dd$Comp) <- levels(d$Comp) <- c("Face", "Voice")


xyplot(2 * scale ~ StimLev, dd, groups = Comp, subset = subID == "6",
	subscripts = TRUE, ylab = "d'", xlab = "Gender Scale", 
	par.settings = list(superpose.symbol = list(pch = 16, col = c("red", "blue")),
						superpose.line = list(col = c("red", "blue"))),
	panel = function(x, y, subscripts, groups, ...){
		panel.superpose(x, y, subscripts, groups, type = "smooth", lwd = 2)
		panel.superpose(x, y, subscripts, groups)
		panel.text(0.5, -0.55, "\u2640")
		panel.text(19, -0.55, "\u2642")
		},
	auto.key = list(title = "Contribution", cex = 0.8, x = 0.1, y = 0.9
))

```

## 1C

```{r 1C, fig.width=6, fig.height=8}
MNS <- 2 * with(d, tapply(scale, list(StimLev, Comp, task), mean))
SEM <- 2 * with(d, tapply(scale, list(StimLev, Comp, task), sd))/sqrt(12)

all.df <- do.call(rbind, apply(MNS, 3, function(m) stack(as.data.frame(m))))
names(all.df) <- c("Scale", "Component")
all.df$SEM <- do.call(rbind, apply(SEM, 3, function(m) stack(as.data.frame(m))))[, 1]
all.df$Task <- factor(strsplit(row.names(all.df), "\\.") |> sapply("[", 1))
all.df$StimLev <- 1:19							
all.df$Task <- factor(all.df$Task, levels = c("Face", "Voice", "Stimulus"))
	
xyplot(Scale ~ StimLev | Component, all.df, groups = Task,
	subscripts = TRUE, ylab = "d'", xlab = "Gender Scale", 
	ylim = c(-0.75, 8),
	par.settings = list(superpose.symbol = list(pch = 16, col = c("red", "blue", "black")),
						superpose.line = list(col = c("red", "blue", "black"))),
	panel = function(x, y, subscripts, groups, ...){
		panel.superpose(x, y, subscripts, groups, type = "smooth", lwd = 2)
		panel.text(0.5, -0.4, "\u2640", cex = 0.85)
		panel.text(19, -0.4, "\u2642", cex = 0.85)
		},
		auto.key = list(title = "Task", cex = 0.8, x = 0.1, y = 0.9), 
	)
```

## 1D

```{r 1D, fig.width = 6, fig.height = 6}
#### get trials from empirical dataset

extract <- function(cond,name="", path = getwd(), cor = (cond >= 3)){
    coord <- paste("^",cond,"_",name,sep="")
    fn <- dir(path)[grep(coord, dir(path))]
    d.lst <- lapply(fn, function(f){
        d <- read.table(paste(path, "/",f, sep = ""), TRUE) 
        if (cor) d$Resp <- 1 - d$Resp
        d
    })
    d.df <- do.call(rbind, d.lst)
    return(d.df)
}


setwd("./data/exp_att/")
data_att.df <- rbind(
    extract(0,"sub1" ), extract(0,"sub2" ), extract(0,"sub3" ),
    extract(0,"sub4" ), extract(0,"sub5" ), extract(0,"sub6" ),
    extract(1,"sub7" ), extract(1,"sub8" ), extract(1,"sub9" ),
    extract(1,"sub10"), extract(1,"sub11"), extract(1,"sub12"),
    extract(2,"sub13"), extract(2,"sub14"), extract(2,"sub15"),
    extract(2,"sub16"), extract(2,"sub17"), extract(2,"sub18"),
    extract(3,"sub19"), extract(3,"sub20"), extract(3,"sub21"),
    extract(3,"sub22"), extract(3,"sub23"), extract(3,"sub24"),
    extract(4,"sub25"), extract(4,"sub26"), extract(4,"sub27"),
    extract(4,"sub28"), extract(4,"sub29"), extract(4,"sub30"),
    extract(5,"sub31"), extract(5,"sub32"), extract(5,"sub33"),
    extract(5,"sub34"), extract(5,"sub35"), extract(5,"sub36") )
setwd("../../")
#           male          female    
#        00  01  02  |  03  04  05  face
#  masc  10  11  12  |  13  14  15  voice
#        20  21  22  |  23  24  25  stim
#        ------------+------------  
#        30  31  32  |  33  34  35  face
#  femi  40  41  42  |  43  44  45  voice
#        50  51  52  |  53  54  55  stim
#
# subject (male = 0, female = 1):             ID_att %% 10 %/% 3
# stimulus (masc = 0, femi = 1):              ID_att %/% 30
# condition (face = 0, voice = 1, stim = 2):  ID_att %% 30 %/% 10
#
ID_att <- rep(0:5,6) + rep(0:5,each = 6)*10
ID_att <- rep(ID_att,each = 1500)

#### modelling

require(MLCM)



att_fac.m <- mlcm(data_att.df[ID_att %% 30 %/% 10 == 0,])
att_voi.m <- mlcm(data_att.df[ID_att %% 30 %/% 10 == 1,])
att_sti.m <- mlcm(data_att.df[ID_att %% 30 %/% 10 == 2,])

lev <-rbind(att_fac.m$pscale[c(18,38)], 
            att_sti.m$pscale[c(18,38)],
            att_voi.m$pscale[c(18,38)])

ci <- rbind(summary(att_fac.m)$se[c(17,35)] * qt(0.975, 11),
            summary(att_sti.m)$se[c(17,35)] * qt(0.975, 11),
            summary(att_voi.m)$se[c(17,35)] * qt(0.975, 11))

wei <- t(apply(lev, 1, function(x) {x / lev[2,]}))

#### plotting

par(cex.lab = 2, mar = c(5, 5, 1, 1) + 0.1)

plot(0, type = "n", xaxt = "n", xlim = c(1,3), ylim = c(0,2),
     xlab = "Condition", ylab = "Relative weights")
axis(1, 1:3, c("Face", "Stimulus", "Voice"), cex.axis = 1.5)
abline(h = 1, col = "gray", lty = 3, lwd = 1.5)
abline(h = 0, col = "gray", lty = 3, lwd = 1.5)

legend("topleft", c("Face", "Voice"), 
       col = c("red", "blue"), lty = 1, cex = 1.5,
       pch = 21, pt.bg = "white", bty = "n", lwd = 1.5)

segments(1:3, wei[,1] - ci[,1], 1:3, wei[,1] + ci[,1], col = 'red', lwd = 1.5)
segments(1:3, wei[,2] - ci[,2], 1:3, wei[,2] + ci[,2], col = 'blue', lwd = 1.5)

lines(wei[,1], lwd = 1.5, cex = 1.5, pch = 21, type = "b", col = "red", bg = "white")
lines(wei[,2], lwd = 1.5, cex = 1.5, pch = 21, type = "b", col = "blue", bg = "white")
```


# Figure 3

```{r 3}
#### get trials from empirical dataset

extract <- function(cond,name="", path = getwd(), cor = (cond >= 3)){
    coord <- paste("^",cond,"_",name,sep="")
    fn <- dir(path)[grep(coord, dir(path))]
    d.lst <- lapply(fn, function(f){
        d <- read.table(paste(path, "/",f, sep = ""), TRUE) 
        if (cor) d$Resp <- 1 - d$Resp
        d
    })
    d.df <- do.call(rbind, d.lst)
    return(d.df)
}

setwd("./data/exp_noi/")
data.df <- rbind(
    extract("Fac","sub1" ), extract("Fac","sub2" ), extract("Fac","sub3" ), 
    extract("Fac","sub4" ), extract("Fac","sub5" ), extract("Fac","sub6" ),
    extract("Voi","sub7" ), extract("Voi","sub8" ), extract("Voi","sub9" ), 
    extract("Voi","sub10"), extract("Voi","sub11"), extract("Voi","sub12"),
    extract("Sti","sub13"), extract("Sti","sub14"), extract("Sti","sub15"),
    extract("Sti","sub16"), extract("Sti","sub17"), extract("Sti","sub18") 
)
setwd("../../")
#     male          female    
#  00  01  02  |  03  04  05  face
#  10  11  12  |  13  14  15  voice
#  20  21  22  |  23  24  25  stim
#
# subject (male = 0, female = 1):             ID %% 10 %/% 3
# condition (face = 0, voice = 1, stim = 2):  ID %% 30 %/% 10
#
ID <- rep(0:5,3) + rep(0:2,each = 6)*10
ID <- rep(ID,each = 1500)

data.df$ID <- ID


#### functions to simulate responses + apply the same model as empirical data

sim_noi <- function(sim.df, att_w) {
    n_1 <- sim.df$Vn/100
    n_2 <- sim.df$An/100
    
    p_1 <- 1-n_1
    p_2 <- 1-n_2
    
    v_1 <- 1/p_1
    v_2 <- 1/p_2
    
    n1 <- 1/rnorm(nrow(sim.df), 0, v_1)
    n2 <- 1/rnorm(nrow(sim.df), 0, v_2)
    
    w_1 <- n1**2/(n1**2 + n2**2)
    w_2 <- n2**2/(n1**2 + n2**2)
    
    sim.df$d1 <- (sim.df[, 2] - sim.df[, 3] + 1/n1) * w_1 *    att_w
    sim.df$d2 <- (sim.df[, 4] - sim.df[, 5] + 1/n2) * w_2 * (1-att_w)
    sim.df$Delta <- sim.df$d1 + sim.df$d2 + rnorm(nrow(sim.df), 0, 1)
    sim.df$simResp <- as.integer(sim.df$Delta >= 0)
    
    return(cbind(simResp = sim.df$simResp, sim.df[,1:8]))
}


noise_glm_sim <- function(data.df, ID, by = NA, exp1=2, exp2=1,
                          i1=c(.10, .35, .65, .95), i2=c(.05, .35, .65, .95)){
    
    data.df <- rbind(
        sim_noi(data.df[ID %% 30 %/% 10 == 0,], att_w = .6),
        sim_noi(data.df[ID %% 30 %/% 10 == 1,], att_w = .4),
        sim_noi(data.df[ID %% 30 %/% 10 == 2,], att_w = .5)
    )
    
    data.df <- subset(data.df, select = -c(Resp))
    
    colnames(data.df)[1] <- "Resp"
    
    Vlevs <- c(10,50,75,90)
    Alevs <- c(10,50,75,90)
    data.df$Vn <- (0:3)[match(data.df$Vn,Vlevs)]
    data.df$An <- (0:3)[match(data.df$An,Alevs)]
    data.df$VAn  <- as.factor(data.df$Vn*4 + data.df$An + 1)
    
    dim1 <- substr(colnames(data.df)[2], 1, nchar(colnames(data.df)[2])-1)
    dim2 <- substr(colnames(data.df)[4], 1, nchar(colnames(data.df)[4])-1)
    
    # subsample
    if (all(is.na(by))) by = rep(TRUE,nrow(data.df))
    newdata.df <- data.df[by,]
    
    ntri <- nrow(newdata.df)
    newdata.df$VAn <- as.factor(newdata.df$VAn)
    nlev <- length(levels(newdata.df$VAn))
    
    glm.m <- matrix(nrow = ntri, ncol = 3)
    colnames(glm.m) <- c("Resp",paste("d", dim1, sep=""),paste("d", dim2, sep=""))
    glm.m[,1] <- newdata.df$Resp
    glm.m[,2] <- i1[newdata.df[,2]]**exp1 - i2[newdata.df[,3]]**exp1
    glm.m[,3] <- i1[newdata.df[,4]]**exp2 - i2[newdata.df[,5]]**exp2
    glm.df <- as.data.frame(glm.m)
    glm.df$VAn <-newdata.df$VAn
    
    n <- colnames(glm.df)
    
    # initial model
    model <- as.formula(paste(n[1],'~',n[2], '+', n[3], '+ 0'))
    ini.glm <- glm(model, data = glm.df[glm.df$VAn == 1,], family = binomial('probit'))
    
    
    trials <- list()
    for(x in 1:length(ini.glm$coefficients)){
        trials[[x]] <- ini.glm$coefficients[x] * glm.df[,x+1]
    }
    trials.df <- do.call("cbind", trials)
    
    noi <- list()
    for(b in 1:length(ini.glm$coefficients)){
        noi[[b]] <- matrix(data =  0, nrow = ntri, ncol = nlev)
        for (t in 1:ntri){
            noi[[b]][t, match(newdata.df$VAn[t], levels(newdata.df$VAn))] <- trials.df[t,b]
        }
    }
    noi.m <- cbind(newdata.df$Resp, do.call("cbind", noi))
    colnames(noi.m) <- c('Resp',
                         paste('N', 1:10, "_",
                               rep(names(ini.glm$coefficients), each = 10), sep = ""))
    
    noi.df <- as.data.frame(noi.m)
    n <- colnames(noi.m)
    model <- as.formula(paste(n[1],'~',paste(n[2:length(n)],collapse = '+'),'+ 0'))
    noi.glm <- glm(model, data = noi.df, family = binomial('probit'))
    
    noi.glm$scales_noi <- noi.glm$coefficients
    noi.glm$scales_ini <- ini.glm$coefficients
    
    return(c(ini.glm$coefficients, noi.glm$coefficients))
}


#### get simulated results

fac_filter <- ID %% 30 %/% 10 == 0
voi_filter <- ID %% 30 %/% 10 == 1
sti_filter <- ID %% 30 %/% 10 == 2

mean_ci <- function(x) {
    m <- mean(x)
    n <- length(x)
    me_95 <- qt(0.05/2, df = (n-1), lower.tail = FALSE) * sd(x) / sqrt(n)
    return(c(mean = m, ci_95_low = m - me_95, ci_95_high = m + me_95))
}

set.seed(42)

test_noi <- apply(replicate(25, noise_glm_sim(data.df, ID, fac_filter)), 1, 'mean_ci')
```

## 3AB

```{r 3A, fig.width = 9, fig.height = 6}

scale <- 0:3

opar <- par(mfrow = c(1, 2), mar = c(mar=c(1.1, 3.1, 4.1, 2.1)), mgp = c(1,1,0))

plot(0, type = 'n', xlim = c(0, 3), ylim = c(0,8.5),
     yaxt = 'n', xaxt = 'n',cex.lab = 1.5,
     xlab = '', ylab = "simulated d'", main = 'noise in attended modality')

legend("topleft", c("attended no noise", "attended noise", "unattended no noise", "unattended noise"), 
       lty = c(2,1,2,1), col = c("red", "red", "blue", "blue"), lwd = 2, bty = "n",
       x.intersp = 0.5, text.width = 0.01,
       seg.len = 1.5)

polygon(c(scale, rev(scale)),
        c(    scale * test_noi[2,2] * 2,
          rev(scale * test_noi[3,2] * 2)),
        col = rgb(0,0,1,.1), border = NA)
polygon(c(scale, rev(scale)),
        c(    scale * test_noi[2,2]  * test_noi[2, 5] * 2,
          rev(scale * test_noi[3,2]  * test_noi[3, 5] * 2)),
        col = rgb(0,0,1,.1), border = NA)
polygon(c(scale, rev(scale)),
        c(    scale * test_noi[2,1] * 2,
          rev(scale * test_noi[3,1] * 2)),
        col = rgb(1,0,0,.1), border = NA)
polygon(c(scale, rev(scale)),
        c(    scale * test_noi[2,1]  * test_noi[2,15] * 2,
          rev(scale * test_noi[3,1]  * test_noi[3,15] * 2)),
        col = rgb(1,0,0,.1), border = NA)

abline(h = 0, lty = 3, col = 'black', lwd = 2)
lines(scale, scale * test_noi[1,2] * 2, col = 'blue', lty = 2, lwd = 3)
lines(scale, scale * test_noi[1,1] * 2, col = 'red' , lty = 2, lwd = 3)

lines(scale, scale * test_noi[1,2] * test_noi[1, 5] * 2, col = 'blue', lty = 1, lwd = 3)
lines(scale, scale * test_noi[1,1] * test_noi[1,15] * 2, col = 'red' , lty = 1, lwd = 3)


plot(0, type = 'n', xlim = c(0, 3), ylim = c(0,8.5),
     yaxt = 'n', xaxt = 'n',cex.lab = 1.5,
     xlab = '', ylab = "simulated d'", main = 'noise in unattended modality')

polygon(c(scale, rev(scale)),
        c(    scale * test_noi[2,2] * 2,
          rev(scale * test_noi[3,2] * 2)),
        col = rgb(0,0,1,.1), border = NA)
polygon(c(scale, rev(scale)),
        c(    scale * test_noi[2,2]  * test_noi[2, 9] * 2,
          rev(scale * test_noi[3,2]  * test_noi[3, 9] * 2)),
        col = rgb(0,0,1,.1), border = NA)
polygon(c(scale, rev(scale)),
        c(    scale * test_noi[2,1] * 2,
          rev(scale * test_noi[3,1] * 2)),
        col = rgb(1,0,0,.1), border = NA)
polygon(c(scale, rev(scale)),
        c(    scale * test_noi[2,1]  * test_noi[2,19] * 2,
          rev(scale * test_noi[3,1]  * test_noi[3,19] * 2)),
        col = rgb(1,0,0,.1), border = NA)

abline(h = 0, lty = 3, col = 'black', lwd = 2)
lines(scale, scale * test_noi[1,2] * 2, col = 'blue', lty = 2, lwd = 3)
lines(scale, scale * test_noi[1,1] * 2, col = 'red' , lty = 2, lwd = 3)

lines(scale, scale * test_noi[1,2] * test_noi[1, 9] * 2, col = 'blue', lty = 1, lwd = 3)
lines(scale, scale * test_noi[1,1] * test_noi[1,19] * 2, col = 'red' , lty = 1, lwd = 3)
```

## 3CDE

```{r 3BCD, fig.width = 5, fig.height = 10}
scale <- 1:4
opar <- par(mfrow = c(3,1), cex.main = 1.75, cex.lab = 2, mar = c(3, 5, 2, 1))

plot(0, type = 'n', xlim = c(1, 4), ylim = c(0,2),
     cex.lab = 1.5,
     xlab = '', ylab = "relative weight", main = 'noise in attended modality')

abline(h = 0, lty = 3,lwd = 2, col = 'black')
abline(h = 1, lty = 3,lwd = 2, col = 'black')

polygon(c(scale, rev(scale)),
        c(    test_noi[2,c( 3, 4, 5, 6)],
          rev(test_noi[3,c( 3, 4, 5, 6)])),
        col = rgb(0,0,1,.1), border = NA)
polygon(c(scale, rev(scale)),
        c(    test_noi[2,c(13,14,15,16)],
          rev(test_noi[3,c(13,14,15,16)])),
        col = rgb(1,0,0,.1), border = NA)

lines(scale,  test_noi[1,c( 3, 4, 5, 6)], col = 'blue', type = 'b', lwd = 3)
lines(scale,  test_noi[1,c(13,14,15,16)], col = 'red',  type = 'b', lwd = 3)

plot(0, type = 'n', xlim = c(1, 4), ylim = c(0,2),
     cex.lab = 1.5,
     xlab = '', ylab = "relative weight", main = 'noise in unattended modality')

abline(h = 0, lty = 3, lwd = 2, col = 'black')
abline(h = 1, lty = 3, lwd = 2, col = 'black')

polygon(c(scale, rev(scale)),
        c(    test_noi[2,c( 3, 7, 9,11)],
          rev(test_noi[3,c( 3, 7, 9,11)])),
        col = rgb(0,0,1,.1), border = NA)
polygon(c(scale, rev(scale)),
        c(    test_noi[2,c(13,17,19,21)],
          rev(test_noi[3,c(13,17,19,21)])),
        col = rgb(1,0,0,.1), border = NA)

lines(scale,  test_noi[1,c( 3, 7, 9,11)], col = 'blue', type = 'b', lwd = 3)
lines(scale,  test_noi[1,c(13,17,19,21)], col = 'red',  type = 'b', lwd = 3)

plot(0, type = 'n', xlim = c(1, 4), ylim = c(0,2),
     cex.lab = 1.5,
     xlab = '', ylab = "relative weight", main = 'noise in both modalities')

abline(h = 0, lty = 3, lwd = 2, col = 'black')
abline(h = 1, lty = 3, lwd = 2, col = 'black')

polygon(c(scale, rev(scale)),
        c(    test_noi[2,c( 3, 8,10,12)],
          rev(test_noi[3,c( 3, 8,10,12)])),
        col = rgb(0,0,1,.1), border = NA)
polygon(c(scale, rev(scale)),
        c(    test_noi[2,c(13,18,20,22)],
          rev(test_noi[3,c(13,18,20,22)])),
        col = rgb(1,0,0,.1), border = NA)

lines(scale,  test_noi[1,c( 3, 8,10,12)], col = 'blue', type = 'b', lwd = 3)
lines(scale,  test_noi[1,c(13,18,20,22)], col = 'red',  type = 'b', lwd = 3)
```

# Figure 4
```{R 4, fig.width = 8, fig.height = 5}

#### get trials from empirical dataset

extract <- function(cond,name="", path = getwd(), cor = (cond >= 3)){
    coord <- paste("^",cond,"_",name,sep="")
    fn <- dir(path)[grep(coord, dir(path))]
    d.lst <- lapply(fn, function(f){
        d <- read.table(paste(path, "/",f, sep = ""), TRUE) 
        if (cor) d$Resp <- 1 - d$Resp
        d
    })
    d.df <- do.call(rbind, d.lst)
    return(d.df)
}

setwd("./data/exp_noi/")
data.df <- rbind(
  extract("Fac","sub1" ), extract("Fac","sub2" ), extract("Fac","sub3" ), 
  extract("Fac","sub4" ), extract("Fac","sub5" ), extract("Fac","sub6" ),
  extract("Voi","sub7" ), extract("Voi","sub8" ), extract("Voi","sub9" ), 
  extract("Voi","sub10"), extract("Voi","sub11"), extract("Voi","sub12"),
  extract("Sti","sub13"), extract("Sti","sub14"), extract("Sti","sub15"),
  extract("Sti","sub16"), extract("Sti","sub17"), extract("Sti","sub18") 
)
setwd("../../")
#     male          female    
#  00  01  02  |  03  04  05  face
#  10  11  12  |  13  14  15  voice
#  20  21  22  |  23  24  25  stim
#
# subject (male = 0, female = 1):             ID %% 10 %/% 3
# condition (face = 0, voice = 1, stim = 2):  ID %% 30 %/% 10
#
ID <- rep(0:5,3) + rep(0:2,each = 6)*10
ID <- rep(ID,each = 1500)

data.df$ID <- ID

data.df$Vn <- (0:3)[match(data.df$Vn,c(10,50,75,90))]
data.df$An <- (0:3)[match(data.df$An,c(10,50,75,90))]
data.df$VAn  <- as.factor(data.df$Vn*4 + data.df$An + 1)
data.df$cond  <- as.factor(ID %% 30 %/% 10)
data.df$Resp <- as.factor(data.df$Resp)

require(MLCM)
plot.mlcm.df <- function (x, clr = NULL, idObs = FALSE, ...) 
{
  if(!is.factor(x$Resp)) x$Resp <- factor(x$Resp, levels = unique(x$Resp))
  # check to order so that all proportions map to upper left diagonal
  sw <- (x[, 2] > x[, 3]) | ((x[, 2] == x[, 3]) & (x[, 4] > x[, 5]))
  xl <- levels(x$Resp)
  x[sw, ] <- x[sw, c(1, 3:2, 5:4)]
  x$Resp <- unclass(x$Resp) - 1
  x[sw, 1] <- 1 - x[sw, 1]
  x$Resp <- factor(xl[x$Resp + 1], levels = xl)
  mx <- max(x[, -1])
  x$IntAct <- with(x, factor(x[, 2]):factor(x[, 4]):factor(x[, 
                                                             3]):factor(x[, 5]))
  x.tab <- with(x, table(Resp, IntAct))
  x.prop <- 1 - apply(x.tab, 2, function(x) x/sum(x)) #x.tab/max(x.tab)
  x.mat <- matrix(x.prop[2, ], ncol = mx^2, byrow = TRUE)
  x.mat[col(x.mat) < row(x.mat)] <- NA
  clr <- if (is.null(clr)) {
    nr <- max(colSums(x.tab))
    stp <- trunc(83/nr)
    grey(seq(0, nr * stp, stp)/100)
  }
  else clr
  sl <- seq_len(mx)
  xy <- seq(0.5, mx + 0.5, len = mx^2 + 1)
  if (idObs) diag(x.mat) <- 0.5
  pmar <- par("mar")
  opar <- par(mar = pmar + c(1, 1, 0, 0), mgp = c(1.75, .75, 
                                                  0))
  image(xy, xy, x.mat, col = clr, axes = FALSE, ...)
  box()
  abline(v = sl + 0.5, h = sl + 0.5)
  axis(1, at = sl, tick = FALSE, cex.axis = 1) # cex.axis was 1.2
  axis(2, at = sl, tick = FALSE, cex.axis = 1) # cex.axis was 1.2
  axis(3, at = 0:1 + 0.5, labels = range(sl), cex.axis = 0.9, 
       mgp = c(1, 0.75, 0))
  axis(4, at = 0:1 + 0.5, labels = range(sl), cex.axis = 0.9, 
       las = 2, mgp = c(1, 0.75, 0))
  par(opar)
  invisible()
}

simVid.df <- data.df
simAid.df <- data.df
simVid.df$Resp <- (simVid.df$V1 >= simVid.df$V2)
simAid.df$Resp <- (simAid.df$A1 >= simAid.df$A2)

clr <- grey(seq(1, 224)/256)

cond <- 0


opar <- par(mfrow = c(3,5),mar = c(2,4,4,2), cex.main = .9)
plot(as.mlcm.df(simVid.df[, 1:5]), clr = clr, idObs = TRUE, xlab = '', ylab = '', main = 'Ideal visual')
plot(0, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n',ann = F)
plot(as.mlcm.df(data.df[data.df$cond == cond & data.df$VAn == 2, 1:5],clr = clr), xlab = '', ylab = '', main = 'Auditory noise: 50')
plot(as.mlcm.df(data.df[data.df$cond == cond & data.df$VAn == 3, 1:5],clr = clr), xlab = '', ylab = '', main = 'Auditory noise: 75')
plot(as.mlcm.df(data.df[data.df$cond == cond & data.df$VAn == 4, 1:5],clr = clr), xlab = '', ylab = '', main = 'Auditory noise: 90')

plot(0, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n',ann = F)
lgd = rep(NA, 9)
lgd[c(1 ,9)] = c('100%', '0%')
legend(x = 1.3, y = 1, legend = lgd, bty = 'n', x.intersp = .1,
       fill = colorRampPalette(colors =c("white","black"))(11),
       border = NA, y.intersp = 0.5, cex = 1, xpd=NA)

legend(0.1, .8, cex = 1, xpd=TRUE, bty = 'n', border = NA,
       expression('Proportion of',
                  paste('stimulus ', S[kl], ' chosen'),
                  'as more masculine'))

plot(as.mlcm.df(data.df[data.df$cond == cond & data.df$VAn == 1, 1:5],clr = clr), xlab = '', ylab = '', main = 'Low noise')
text(2.5,c(-1.4,-2.2, -3), xpd = NA,
     expression(paste("Stimulus ", S[ij]),
                "Visual gender i",
                "Auditory gender j"))
text(c(7.6,6.8,6),2.5,srt=-90, xpd = NA,
     expression(paste("Stimulus ", S[kl]),
                "Visual gender k",
                "Auditory gender l"))

plot(0, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n',ann = F)
plot(0, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n',ann = F)
plot(0, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n',ann = F)

plot(as.mlcm.df(simAid.df[, 1:5]), clr = clr, idObs = TRUE, xlab = '', ylab = '', main = 'Ideal auditory')
plot(0, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n',ann = F)
plot(as.mlcm.df(data.df[data.df$cond == cond & data.df$VAn ==  5, 1:5],clr = clr), xlab = '', ylab = '', main = 'Visual noise: 50')
plot(as.mlcm.df(data.df[data.df$cond == cond & data.df$VAn ==  9, 1:5],clr = clr), xlab = '', ylab = '', main = 'Visual noise: 75')
plot(as.mlcm.df(data.df[data.df$cond == cond & data.df$VAn == 13, 1:5],clr = clr), xlab = '', ylab = '', main = 'Visual noise: 95')
par(opar)

```

# Figure 5

## 5A-I

```{R 5AI, fig.width = 10, fig.height = 10}

#### get trials from empirical dataset

extract <- function(cond,name="", path = getwd(), cor = (cond >= 3)){
    coord <- paste("^",cond,"_",name,sep="")
    fn <- dir(path)[grep(coord, dir(path))]
    d.lst <- lapply(fn, function(f){
        d <- read.table(paste(path, "/",f, sep = ""), TRUE) 
        if (cor) d$Resp <- 1 - d$Resp
        d
    })
    d.df <- do.call(rbind, d.lst)
    return(d.df)
}

setwd("./data/exp_noi/")
data.df <- rbind(
  extract("Fac","sub1" ), extract("Fac","sub2" ), extract("Fac","sub3" ), 
  extract("Fac","sub4" ), extract("Fac","sub5" ), extract("Fac","sub6" ),
  extract("Voi","sub7" ), extract("Voi","sub8" ), extract("Voi","sub9" ), 
  extract("Voi","sub10"), extract("Voi","sub11"), extract("Voi","sub12"),
  extract("Sti","sub13"), extract("Sti","sub14"), extract("Sti","sub15"),
  extract("Sti","sub16"), extract("Sti","sub17"), extract("Sti","sub18") 
)
setwd("../../")
#     male          female    
#  00  01  02  |  03  04  05  face
#  10  11  12  |  13  14  15  voice
#  20  21  22  |  23  24  25  stim
#
# subject (male = 0, female = 1):             ID %% 10 %/% 3
# condition (face = 0, voice = 1, stim = 2):  ID %% 30 %/% 10
#
ID <- rep(0:5,3) + rep(0:2,each = 6)*10
ID <- rep(ID,each = 1500)

data.df$ID <- ID


#### modelling apparatus

require(lme4)

noise_glm <- function(data.df, ID, by = NA, exp1=2, exp2=1, i1=c(.10, .35, .65, .95),
                      i2=c(.05, .35, .65, .95)){
    
    Vlevs <- c(10,50,75,90)
    Alevs <- c(10,50,75,90)
    data.df$Vn <- (0:3)[match(data.df$Vn,Vlevs)]
    data.df$An <- (0:3)[match(data.df$An,Alevs)]
    data.df$VAn  <- as.factor(data.df$Vn*4 + data.df$An + 1)
    
    dim1 <- substr(colnames(data.df)[2], 1, nchar(colnames(data.df)[2])-1)
    dim2 <- substr(colnames(data.df)[4], 1, nchar(colnames(data.df)[4])-1)
    
    # subsample
    if (all(is.na(by))) by = rep(TRUE,nrow(data.df))
    newdata.df <- data.df[by,]
    
    ntri <- nrow(newdata.df)
    newdata.df$VAn <- as.factor(newdata.df$VAn)
    nlev <- length(levels(newdata.df$VAn))
    
    glmm.m <- matrix(nrow = ntri, ncol = 3)
    colnames(glmm.m) <- c("Resp",paste("d", dim1, sep=""),paste("d", dim2, sep=""))
    glmm.m[,1] <- newdata.df$Resp
    glmm.m[,2] <- i1[newdata.df[,2]]**exp1 - i2[newdata.df[,3]]**exp1
    glmm.m[,3] <- i1[newdata.df[,4]]**exp2 - i2[newdata.df[,5]]**exp2
    glmm.df <- as.data.frame(glmm.m)
    glmm.df$s <- as.factor(ID[by])
    glmm.df$VAn <-newdata.df$VAn
    
    n <- colnames(glmm.df)
    
    # initial model
    model <- as.formula(paste(n[1],'~',n[2], '+', n[3], '+ 0 + (',n[2],'+0|s)+(',n[3],'+0|s)'))
    ini.glmm <- glmer(model, data = glmm.df[glmm.df$VAn == 1,], family = binomial('probit'))
    
    
    trials <- list()
    for(x in 1:length(fixef(ini.glmm))){
      trials[[x]] <- (fixef(ini.glmm)[x]+ranef(ini.glmm)$s[glmm.df$s,x]) *  glmm.df[,x+1]
    }
    trials.df <- do.call("cbind", trials)
    
    noi <- list()
    for(b in 1:length(fixef(ini.glmm))){
        noi[[b]] <- matrix(data =  0, nrow = ntri, ncol = nlev)
        for (t in 1:ntri){
            noi[[b]][t, match(newdata.df$VAn[t], levels(newdata.df$VAn))] <- trials.df[t,b]
        }
    }
    noi.m <- cbind(newdata.df$Resp, do.call("cbind", noi))
    colnames(noi.m) <- c('Resp',
                         paste('N', 1:10, "_", rep(names(fixef(ini.glmm)), each = 10),sep = ""))
    
    noi.df <- as.data.frame(noi.m)
    n <- colnames(noi.m)
    model <- as.formula(paste(n[1],'~',paste(n[2:length(n)],collapse = '+'),'+ 0'))
    noi.glm <- glm(model, data = noi.df, family = binomial('probit'))
    
    noi.glm$scales_noi <- noi.glm$coefficients
    noi.glm$scales_ini <- fixef(ini.glmm)
    noi.glm$noi.df     <- noi.df
    
    return(noi.glm)
}


#### get models

fac_filter <- ID %% 30 %/% 10 == 0
voi_filter <- ID %% 30 %/% 10 == 1
sti_filter <- ID %% 30 %/% 10 == 2


fac_noi <- noise_glm(data.df, ID, fac_filter)
voi_noi <- noise_glm(data.df, ID, voi_filter)
sti_noi <- noise_glm(data.df, ID, sti_filter)

#### plot results

layout(matrix(1:9, nrow = 3, byrow = TRUE))
opar <- par(mgp = c(2,1,0), mar = c(3,3.5,2,1), cex.main = 2, cex.lab = 2)
ylim <- c(-1.25,4.3)
xlab <- '% noise'
noi_int <- c(10,50,75,90)

# Face task
ci <- summary(fac_noi)$coefficients[,2] * qt(0.975, 5)
plot(0, type='n', xlim=c(0,100), ylim=ylim, cex.lab=1.5, xlab=xlab, xaxt = 'n',
     ylab='weights in Face task', main="visual noise")

axis(1, at=noi_int, labels = noi_int)
abline(h=c(0,1), lty = 3, lwd = 1.5, col = 'black')
segments(noi_int, fac_noi$scales_noi[c(1,5,7,9)   ] - ci[c(1,5,7,9)], noi_int,
         fac_noi$scales_noi[c(1,5,7,9)   ] + ci[c(1,5,7,9)], col = 'red', lwd = 1.5)
segments(noi_int, fac_noi$scales_noi[c(1,5,7,9)+10] - ci[c(1,5,7,9)+10], noi_int,
         fac_noi$scales_noi[c(1,5,7,9)+10] + ci[c(1,5,7,9)+10], col = 'blue', lwd = 1.5)
lines(noi_int, fac_noi$scales_noi[c(1,5,7,9)   ], type = 'b', lwd = 1.5,
      pch = 21, col = 'red', bg = 'white')
lines(noi_int, fac_noi$scales_noi[c(1,5,7,9)+10], type = 'b', lwd = 1.5,
      pch = 21, col = 'blue', bg = 'white')

plot(0, type='n', xlim=c(0,100), ylim=ylim, cex.lab=1.5, xlab=xlab, xaxt = 'n',
     ylab='', main="auditory noise")
axis(1, at=noi_int, labels = noi_int)
abline(h=c(0,1),lty = 3, lwd = 1.5, col = 'black')
segments(noi_int,fac_noi$scales_noi[1:4] - ci[1:4], noi_int,
         fac_noi$scales_noi[1:4] + ci[1:4], col = 'red', lwd = 1.5)
segments(noi_int, fac_noi$scales_noi[(1:4)+10] - ci[(1:4)+10], noi_int,
         fac_noi$scales_noi[(1:4)+10] + ci[(1:4)+10], col = 'blue', lwd = 1.5)
lines(noi_int, fac_noi$scales_noi[ 1:4    ], type = 'b', lwd = 1.5, pch = 21,
      col = 'red', bg = 'white')
lines(noi_int, fac_noi$scales_noi[(1:4)+10], type = 'b', lwd = 1.5, pch = 21,
      col = 'blue', bg = 'white')

plot(0, type='n', xlim=c(0,100), ylim=ylim, cex.lab=1.5, xlab=xlab, xaxt = 'n',
     ylab='', main="bimodal noise")
axis(1, at=noi_int, labels = noi_int)
abline(h=c(0,1),lty = 3, lwd = 1.5, col = 'black')
segments(noi_int,fac_noi$scales_noi[c(1,6,8,10)] - ci[c(1,6,8,10)], noi_int,
         fac_noi$scales_noi[c(1,6,8,10)] + ci[c(1,6,8,10)], col = 'red', lwd = 1.5)
segments(noi_int, fac_noi$scales_noi[c(1,6,8,10)+10] - ci[c(1,6,8,10)+10], noi_int,
         fac_noi$scales_noi[c(1,6,8,10)+10] + ci[c(1,6,8,10)+10], col = 'blue', lwd = 1.5)
lines(noi_int, fac_noi$scales_noi[c(1,6,8,10)   ], type = 'b', lwd = 1.5, pch = 21,
      col = 'red', bg = 'white')
lines(noi_int, fac_noi$scales_noi[c(1,6,8,10)+10], type = 'b', lwd = 1.5, pch = 21,
      col = 'blue', bg = 'white')

# Voice task
ci <- summary(voi_noi)$coefficients[,2] * qt(0.975, 5)
plot(0, type='n', xlim=c(0,100), ylim=ylim, cex.lab=1.5, xlab=xlab, xaxt = 'n',
     ylab='weights in voice task', main="")
axis(1, at=noi_int, labels = noi_int)
abline(h=c(0,1), lty = 3, lwd = 1.5, col = 'black')
segments(noi_int, voi_noi$scales_noi[c(1,5,7,9)   ] - ci[c(1,5,7,9)], noi_int,
         voi_noi$scales_noi[c(1,5,7,9)   ] + ci[c(1,5,7,9)], col = 'red', lwd = 1.5)
segments(noi_int, voi_noi$scales_noi[c(1,5,7,9)+10] - ci[c(1,5,7,9)+10], noi_int,
         voi_noi$scales_noi[c(1,5,7,9)+10] + ci[c(1,5,7,9)+10], col = 'blue', lwd = 1.5)
lines(noi_int, voi_noi$scales_noi[c(1,5,7,9)   ], type = 'b', lwd = 1.5, pch = 21,
      col = 'red', bg = 'white')
lines(noi_int, voi_noi$scales_noi[c(1,5,7,9)+10], type = 'b', lwd = 1.5, pch = 21,
      col = 'blue', bg = 'white')

plot(0, type='n', xlim=c(0,100), ylim=ylim, cex.lab=1.5, xlab=xlab, xaxt = 'n',
     ylab='', main="")
axis(1, at=noi_int, labels = noi_int)
abline(h=c(0,1),lty = 3, lwd = 1.5, col = 'black')
segments(noi_int,voi_noi$scales_noi[1:4] - ci[1:4], noi_int,
         voi_noi$scales_noi[1:4] + ci[1:4], col = 'red', lwd = 1.5)
segments(noi_int, voi_noi$scales_noi[(1:4)+10] - ci[(1:4)+10], noi_int,
         voi_noi$scales_noi[(1:4)+10] + ci[(1:4)+10], col = 'blue', lwd = 1.5)
lines(noi_int, voi_noi$scales_noi[ 1:4    ], type = 'b', lwd = 1.5, pch = 21,
      col = 'red', bg = 'white')
lines(noi_int, voi_noi$scales_noi[(1:4)+10], type = 'b', lwd = 1.5, pch = 21, 
      col = 'blue', bg = 'white')

plot(0, type='n', xlim=c(0,100), ylim=ylim, cex.lab=1.5, xlab=xlab, xaxt = 'n',
     ylab='', main="")
axis(1, at=noi_int, labels = noi_int)
abline(h=c(0,1),lty = 3, lwd = 1.5, col = 'black')
segments(noi_int,voi_noi$scales_noi[c(1,6,8,10)] - ci[c(1,6,8,10)], noi_int,
         voi_noi$scales_noi[c(1,6,8,10)] + ci[c(1,6,8,10)], col = 'red', lwd = 1.5)
segments(noi_int, voi_noi$scales_noi[c(1,6,8,10)+10] - ci[c(1,6,8,10)+10], noi_int,
         voi_noi$scales_noi[c(1,6,8,10)+10] + ci[c(1,6,8,10)+10], col = 'blue', lwd = 1.5)
lines(noi_int, voi_noi$scales_noi[c(1,6,8,10)   ], type = 'b', lwd = 1.5, pch = 21,
      col = 'red', bg = 'white')
lines(noi_int, voi_noi$scales_noi[c(1,6,8,10)+10], type = 'b', lwd = 1.5, pch = 21,
      col = 'blue', bg = 'white')

# Stimulus task
ci <- summary(sti_noi)$coefficients[,2] * qt(0.975, 5)
plot(0, type='n', xlim=c(0,100), ylim=ylim, cex.lab=1.5, xlab=xlab, xaxt = 'n',
     ylab='weights in stimulus task', main="")
axis(1, at=noi_int, labels = noi_int)
abline(h=c(0,1), lty = 3, lwd = 1.5, col = 'black')
segments(noi_int, sti_noi$scales_noi[c(1,5,7,9)   ] - ci[c(1,5,7,9)], noi_int,
         sti_noi$scales_noi[c(1,5,7,9)   ] + ci[c(1,5,7,9)], col = 'red', lwd = 1.5)
segments(noi_int, sti_noi$scales_noi[c(1,5,7,9)+10] - ci[c(1,5,7,9)+10], noi_int,
         sti_noi$scales_noi[c(1,5,7,9)+10] + ci[c(1,5,7,9)+10], col = 'blue', lwd = 1.5)
lines(noi_int, sti_noi$scales_noi[c(1,5,7,9)   ], type = 'b', lwd = 1.5, pch = 21,
      col = 'red', bg = 'white')
lines(noi_int, sti_noi$scales_noi[c(1,5,7,9)+10], type = 'b', lwd = 1.5, pch = 21,
      col = 'blue', bg = 'white')

plot(0, type='n', xlim=c(0,100), ylim=ylim, cex.lab=1.5, xlab=xlab, xaxt = 'n',
     ylab='', main="")
axis(1, at=noi_int, labels = noi_int)
abline(h=c(0,1),lty = 3, lwd = 1.5, col = 'black')
segments(noi_int,sti_noi$scales_noi[1:4] - ci[1:4], noi_int,
         sti_noi$scales_noi[1:4] + ci[1:4], col = 'red', lwd = 1.5)
segments(noi_int, sti_noi$scales_noi[(1:4)+10] - ci[(1:4)+10], noi_int,
         sti_noi$scales_noi[(1:4)+10] + ci[(1:4)+10], col = 'blue', lwd = 1.5)
lines(noi_int, sti_noi$scales_noi[ 1:4    ], type = 'b', lwd = 1.5, pch = 21,
      col = 'red', bg = 'white')
lines(noi_int, sti_noi$scales_noi[(1:4)+10], type = 'b', lwd = 1.5, pch = 21,
      col = 'blue', bg = 'white')

plot(0, type='n', xlim=c(0,100), ylim=ylim, cex.lab=1.5, xlab=xlab,
     xaxt = 'n', ylab='', main="")
axis(1, at=noi_int, labels = noi_int)
abline(h=c(0,1),lty = 3, lwd = 1.5, col = 'black')
segments(noi_int,sti_noi$scales_noi[c(1,6,8,10)] - ci[c(1,6,8,10)], noi_int,
         sti_noi$scales_noi[c(1,6,8,10)] + ci[c(1,6,8,10)], col = 'red', lwd = 1.5)
segments(noi_int, sti_noi$scales_noi[c(1,6,8,10)+10] - ci[c(1,6,8,10)+10], noi_int,
         sti_noi$scales_noi[c(1,6,8,10)+10] + ci[c(1,6,8,10)+10], col = 'blue', lwd = 1.5)
lines(noi_int, sti_noi$scales_noi[c(1,6,8,10)   ], type = 'b', lwd = 1.5, pch = 21,
      col = 'red', bg = 'white')
lines(noi_int, sti_noi$scales_noi[c(1,6,8,10)+10], type = 'b', lwd = 1.5, pch = 21,
      col = 'blue', bg = 'white')